\chapter{Evaluation}\label{chapter:evaluation}

\section{Test setup}

5 users with 10 measurements each, plus 1 with 5.

First: training with the first 9, respectively 4 measurements, then the last measurement as "detection test" on phone only!



\section{Runtime efficiency}

For debugging, we are logging the results and itermediates to an additional database, relatively poor performance of $4.3$ measurements per second on a OnePlus One.

without logging to the database, we can get around $21$ measurements per second, but there are still parallelization improvements possible.

quick test showed, that esp. the learning phase can be done in parallel and scales extremely well. Potential speedup ~4x.

on phone vs. on watch

On Sony Smartwatch 3, performance is proportionally to the processor speed: aprox $1.8$ measurements per second in debugging mode, with potential speedups with parallelization and no logging factor 5x~6x. With a measured Bluetooth transfer rate of ~15KB/s, this is still faster then transfering the sensordata to the phone and back!

\section{Optimal parameters for accuracy}

4 main tunable parameters: windowsize with the peak detection, the peak detection stringency, the DTW window size and the $k$ in knn algorithm.

optimal peak window size at 67 measurements, as calculated in section~TODO

stringency showed best results at 2

dtw parameter expectedly did not improve results with bigger window sizes

$k = 7$ resulted in the best user detection rates

with optimal parameters, we reached an detection rate of 80\%

